### 2014-06-05 ApTranscriptome_TR.Rmd
Clustered topGO GSEA results by GO term semantic similarity for A22 Low and High genes

# Load libraries
library(R.utils)
library(ggplot2)
library(knitr)
library(knitcitations)
library(pander)
library(stringr)
library(data.table)
library(RCurl)
library(plyr)
library(MASS)
library(xtable)
library(methods) # required by `knitcitations` when file is `knit` from command-line
library(reshape2)
library(psych)

@@

```{r GOSemSim}
# similarity among enriched GO terms
A22.GO.term.sim <- termSim(A22.low.gsea$GO.ID, A22.low.gsea$GO.ID, ont = "BP", organism = "fly")
# distance matrix
dist.A22.GO.term.sim <- dist(A22.GO.term.sim)
plot(hclust(dist(A22.GO.term.sim)))

@@

getCurrentSpeciesPosition2<-function(object){
    ans <- NA
    if(length(getSpecieNames(object)) != 0){
        stub<-getStub(object)
        ans<-as.integer(strsplit(stub$getCurrentSpecies(), split = ",")[[1]]) + 1
    }
    return(ans)
}

getCurrentSpeciesPosition2(david.connect)

# obtain Functional Annotation Cluster
A22.high.termCluster <- getClusterReport(david.connect, type = "Term")
summary(A22.high.termCluster)
members(A22.high.termCluster)[[1]]$Term
members(A22.high.termCluster)[[2]]$Term
members(A22.high.termCluster)[[3]]$Term

# calculate Enrichment
geometric_mean <- function(x) exp(mean(log(x)))
-log10(geometric_mean(members(A22.high.termCluster)[[1]]$PValue))
-log10(geometric_mean(members(A22.high.termCluster)[[2]]$PValue))
-log10(geometric_mean(members(A22.high.termCluster)[[3]]$PValue))
-log10(geometric_mean(members(A22.high.termCluster)[[4]]$PValue))
-log10(geometric_mean(members(A22.high.termCluster)[[5]]$PValue))
-log10(geometric_mean(members(A22.high.termCluster)[[6]]$PValue))
-log10(geometric_mean(members(A22.high.termCluster)[[7]]$PValue))
```

>>>>

# Load libraries
library(R.utils)
library(ggplot2)
library(knitr)
library(knitcitations)
library(pander)
library(stringr)
library(data.table)
library(RCurl)
library(plyr)
library(MASS)
library(xtable)
library(methods) # required by `knitcitations` when file is `knit` from command-line
library(reshape2)

@@

```{r GOSemSim}
# similarity among enriched GO terms
A22.low.GO.term.sim <- termSim(A22.low.gsea$GO.ID, A22.low.gsea$GO.ID, ont = "BP", organism = "fly")
# distance matrix
dist.A22.low.GO.term.sim <- dist(A22.low.GO.term.sim)
plot(hclust(dist(A22.low.GO.term.sim)))

A22.high.GO.term.sim <- termSim(A22.high.gsea$GO.ID, A22.high.gsea$GO.ID, ont = "BP", organism = "fly")
# distance matrix
plot(hclust(dist(A22.high.GO.term.sim)))
```

@@

getCurrentSpeciesPosition2<-function(object){
geometric_mean <- function(x) exp(mean(log(x)))
-log10(geometric_mean(members(A22.high.termCluster)[[1]]$PValue))
-log10(geometric_mean(members(A22.high.termCluster)[[2]]$PValue))
-log10(geometric_mean(members(A22.high.termCluster)[[3]]$PValue))
-log10(geometric_mean(members(A22.high.termCluster)[[4]]$PValue))
-log10(geometric_mean(members(A22.high.termCluster)[[5]]$PValue))
-log10(geometric_mean(members(A22.high.termCluster)[[6]]$PValue))
-log10(geometric_mean(members(A22.high.termCluster)[[7]]$PValue))
```
